\vspace{60pt}\\ \huge \bfseries Skedge \\ \vspace{10pt} \Large Smarter course scheduling for our University

### 2016-04-14 analytics/usage.tex
small typo

{\renewcommand{\arraystretch}{1.5}
\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users have linked Skedge to Facebook ($\sim$3.5 per day) \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through its tabs and repeatedly return to it) \\
  a 5\% bounce rate (users interact with the page before leaving) \\
  67\% of visits being were returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing

>>>>

{\renewcommand{\arraystretch}{1.5}
\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users on the platform ($\sim$3.5 per day) \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through its tabs and repeatedly return to it) \\
  a 5\% bounce rate (users interact with the page before leaving) \\
  67\% of visits being returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing
